\section{ASTRI-Horn telescope} 
The ASTRI-Horn telescope is based on a dual mirror system in Schawrzschild-Couder configuration
with a wide field of view (FoV) of 9.6$^\circ$ and a focal length of 2.15 m. 
The primary mirror, 4.3 m diameter, is segmented in 18 hexagonal panels, 
while the secondary mirror, 2.2 m diameter, is a monolitic hemispherical thick glass shell. 
Dedicated measurements  with an optical CCD camera showed that the
point spread function (PSF) has a constant width of a few arcmin
over the whole FoV and that  90\% of the PSF  is containerd in one camera pixel. 

The focal surface camera, has a convex-shaped structure where
photon detection modules (PDMs), that are square flat modules, are symmetrically placed
with angles respect to the telescope axis 
opportunely chosen in order to follow the curvature of the focal plane.
Each PDM, composed of 8$\times$8 side-by-side Silicon photomultipliers (SiPMs), 
is installed on a printed circuit board (PCB)  of the same dimension.
The PCB hosts the front-end electronics (FEE) composed by
 two application specific integrated circuits (ASIC) for the SiPM signal read out,
four Analogue-to-Digital Converters (ADC) and one Field Programmable
Gate Array (FPGA). This FEE-FPGA manages the ASICs slow control,
the generation of local trigger and the data analog-to-digital conversion \cite{Sottile2016}.
 Images of the Polaris Star at different off-axis angles (up to 4.5◦
) have been taken with an optical
CCD camera able to scan the whole FoV, demonstrating that the
point spread function (PSF) has a constant width of a few arcmin
over the whole FoV.
Since the SC optical design typically results in a small
plate scale (37.5 mm/
◦
in the case of ASTRI), the camera at
the focal plane is characterized by compact dimensions over a
large FoV. F Back-End Electronics (BEE) is composed of two main parts that are
a Processing System (PS) and a Programmable Logic (PL). 
It is the main elaboration unit of the camera which
controls and manages the overall system, including data, and
all ancillaries used to perform operations as
the camera thermal regulation, 
the Voltage Distribution management and the time events stamping.
The BEE also provides the functions necessary to
process and transmit the event data as 
obtained by the FEE to an external Data Acquisition 
Workstation responsible for receiving and storing
the data packets(see Sect.4 (\cite{Sottile2016}).
In order to protect the camera sensors from the external
atmospheric environment, an optical-UV transparent
Poly Methyl MethAcrylate (PMMA)  window 
is mounted onto the focal surface support structure covering all the
PDMs.
This window is modeled with the same radius of
curvature of the focal surface (see Sect.2 (\cite{Catalano2018}).
A side emitting Fiber Optics system(FOC) is located  along the PMMA 
circumference. It is illuminated by a Light Emitting Diode (LED) 
system and used for the on-field relative calibration of the gain. 
Its light uniformly illuminates the PDMs units at a controlled intensity.
The ASTRI SST-2M camera
is equipped also with a light-tight lid composed of two petals
mounted onto the backbone structure of the camera. 
This prevents accidental sunlight exposure of the focal surface
detectors, catastrophic in case of direct light reflected
by the mirrors.  
The camera is thermally controlled to keep the
working temperature on the focal plane within the range 13-17$^\circ$C
giving a high gain accuracy. \textcolor{red}{(sarebbe meglio evitare di fare riferimento all'accuratezza richiesto da CTA [pag. 281 del paper di Actis 2011])}.\\

The ASTRI camera electronics (\cite{Sottile2016}) represents an innovative solution, being based on a custom peak-detector operation mode to acquire the SiPM pulses rather than the sampling technique adopted by other cherenkov telescopes. The SiPM  read-out chip, with its signal shaper and peak detector customized for ASTRI, provides high efficiency auto-trigger capability and very fast camera pixel read out. The ASTRI camera trigger is a topological one, activated when a given number of contiguous pixels within a PDM presents a signal above a given photo-electron threshold. Data registered by the ASTRI camera at the occurrence of a trigger condition (scientific event) or when required (calibration or housekeeping data) are then sent to the camera server in which the camera data acquisition software is installed. 
